Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-02-04 paper/main.tex
update GA

We use the original implementation of GECO.\footnote{\url{https://cran.r-project.org/package=CEGO}} %
Although it is never stated in the original paper, the implementation of CEGO
generates a set of initial solutions of size $\minit=10$ by means of a
max-min-distance sequential design: new solutions are added to the set
sequentially by maximizing the minimum distance to solutions already in the
set. These initial solutions are then evaluated on the true fitness function
and the result is used to build the initial surrogate
model. % \citet{ZaeStoBar2014:ppsn} uses \minit=10
Following the authors of
CEGO~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, we use a GA to optimize
\ekhine{}{hay que actualizar essto??}
the surrogate models with population size of 20, crossover rate of 0.5,
mutation rate of $1/n$, tournament selection of size 2 with probability of 0.9,
interchange mutation (i.e., exchanging two randomly selected elements) and
cycle crossover for permutations. To generate each new solution, CEGO runs the
GA using the model as a surrogate of the true fitness function.  The authors of
CEGO used a budget of $10^4$ surrogate-model evaluations for each run of the
GA and we use the same confuguration parameters.% However, with such a setting, a single run of CEGO with a budget of
%$\FEmax=400$ true fitness evaluations requires \emph{more than a week} of
%computation time, which was infeasible for our study. 
%Due to extremely long
%runtimes of CEGO and constraints in our computing system, we set the budget of
%the GA to $10^3$ and we stopped each run of CEGO after 144 hours of CPU-time.
%Although a higher GA budget could improve the results of CEGO reported here,
%our results are similar (and sometimes better) than the ones reported in the
%original papers~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn} due to
%running CEGO with $\FEmax=400$ instead of $\FEmax=200$. We found that
%doubling $\FEmax$ produces a smaller increase in runtime than multiplying the
%GA budget by a factor of $10$. Nevertheless, we caution that choosing a
%different trade-off may lead to different conclusions and more work is needed
%to understand CEGO parameters.

>>>>

We use the original implementation of GECO.\footnote{\url{https://cran.r-project.org/package=CEGO}} %
Although it is never stated in the original paper, the implementation of CEGO
generates a set of initial solutions of size $\minit=10$ by means of a
max-min-distance sequential design: new solutions are added to the set
sequentially by maximizing the minimum distance to solutions already in the
set. These initial solutions are then evaluated on the true fitness function
and the result is used to build the initial surrogate
model. % \citet{ZaeStoBar2014:ppsn} uses \minit=10
Following the authors of
CEGO~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, we use a GA to optimize
the surrogate models with population size of 20, crossover rate of 0.5,
mutation rate of $1/n$, tournament selection of size 2 with probability of 0.9,
interchange mutation (i.e., exchanging two randomly selected elements) and
cycle crossover for permutations. To generate each new solution, CEGO runs the
GA with a budget of $10^4$ evaluations of the model as a surrogate of the true fitness function.  
%and we use the same configuration parameters.% However, with such a setting, a single run of CEGO with a budget of
%$\FEmax=400$ true fitness evaluations requires \emph{more than a week} of
%computation time, which was infeasible for our study. 
%Due to extremely long
%runtimes of CEGO and constraints in our computing system, we set the budget of
%the GA to $10^3$ and we stopped each run of CEGO after 144 hours of CPU-time.
%Although a higher GA budget could improve the results of CEGO reported here,
%our results are similar (and sometimes better) than the ones reported in the
%original papers~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn} due to
%running CEGO with $\FEmax=400$ instead of $\FEmax=200$. We found that
%doubling $\FEmax$ produces a smaller increase in runtime than multiplying the
%GA budget by a factor of $10$. Nevertheless, we caution that choosing a
%different trade-off may lead to different conclusions and more work is needed
%to understand CEGO parameters.
